# Results

# Q1: As economics exploded, what was the development of the 120 years Olympics from 1986 to 2016?

## Pic 1
```{r}
numcount <- olympic_athletes_events %>% 
            group_by(Year, Season) %>%
            summarize(Athletes = length(unique(ID)), 
                      Teams = length(unique(Team)),
                      Sports = length(unique(Sport)))


p1 <- ggplot(numcount, aes(x=Year, y=Athletes, group=Season, color=Season)) +
          geom_point(size=1.8) +
          geom_line() +
          scale_color_manual(values=c("#cbc9e2","#2b8cbe")) +
          xlab("") +  
        annotate("text", x=c(1932,1956,1976,1980),
                 y=c(2000,2750,6800,4700),
                 label=c("L.A. 1932","Melbourne 1956","Montreal 1976","Moscow 1980"),
                 size=2.5) +
        annotate("text",x=c(1916,1942),y=c(9000,9000),
                 label=c("WWI","WWII"), size=3.5, color="sienna1") +
        geom_segment(mapping=aes(x=1914,y=8000,xend=1918,yend=8000),color="sienna1", size=1.5) +
        geom_segment(mapping=aes(x=1939,y=8000,xend=1945,yend=8000),color="sienna1", size=1.5) + 
        theme(legend.position="bottom")
p2 <- ggplot(numcount, aes(x=Year, y=Teams, group=Season, color=Season)) +
        geom_point(size=1.8) +
        geom_line() +
        scale_color_manual(values=c("#cbc9e2","#2b8cbe")) +
        xlab("") +  
        # annotate("text", x=c(1932,1976,1980),
        #          y=c(62,110,85),
        #          label=c("L.A. 1932","Montreal 1976","Moscow 1980"),
        #          size=2.5) + 
        theme(legend.position="bottom")
p3 <- ggplot(numcount, aes(x=Year, y=Sports, group=Season, color=Season)) +
        geom_point(size=1.8) +
        geom_line() +
        scale_color_manual(values=c("#cbc9e2","#2b8cbe")) + 
        theme(legend.position="bottom")

tg <- grid::textGrob('Athletes, Teams and Events over Years', 
                     gp = gpar(fontsize = 13, fontface = 'bold'))
sg <- textGrob('Attendence Number vs Year', 
               gp = gpar(fontsize = 10))
laym <- rbind(rep(1,3), rep(2,3), (3:(3+2)))
plot_list <- list(p1, p2, p3)
g <- c(list(tg),list(sg),plot_list)
grid.arrange(grobs=g,layout_matrix=laym,heights=c(1, 1,10))
```


## Pic 2

```{r}
world <- map_data("world")
losangeles <- olympic_athletes_events %>% 
  filter(Year == 1932 & Season == "Summer") %>%
  group_by(region) %>%
  summarize(LosAngeles = length(unique(ID))) 

# L.A. 1932 Summer Olympic
data1 <- world %>% left_join(
  tibble(region=unique(world$region))) %>% 
    left_join(losangeles, by="region") %>%
  mutate(LosAngeles = ifelse(is.na(LosAngeles), 0, LosAngeles)) 

data1 %>% 
  ggplot(aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = LosAngeles)) +
  labs(title = "The Number of Athletes globally Participated in Los Angeles 1932",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "lightsteelblue4"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="orchid3") +
  theme(plot.title = element_text(size = 10,face="bold.italic", color = "red3"),
        legend.title = element_text(size = 8,face="bold.italic", color = "black"),
        legend.text  = element_text(size = 7,face="italic", color = "black")) 

# Melbourne 1956 Summer Olympic
melbourne <- olympic_athletes_events %>% 
  filter(Year == 1956 & Season == "Summer") %>%
  group_by(region) %>%
  summarize(Melbourne = length(unique(ID)))

data2 <- world %>% left_join(
          tibble(region=unique(world$region))) %>% 
          left_join(melbourne, by="region") %>%
          mutate(Melbourne = ifelse(is.na(Melbourne), 0, Melbourne)) 

data2 %>% 
  ggplot(aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Melbourne)) +
  labs(title = "The Number of Athletes globally Participated in Melbourne 1956",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "lightsteelblue4"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="orchid3") + 
  theme(plot.title = element_text(size = 10,face="bold.italic", color = "red3"),
        legend.title = element_text(size = 8,face="bold.italic", color = "black"),
        legend.text  = element_text(size = 7,face="italic", color = "black")) 

# Montreal 1976 Summer Olympic
montreal <- olympic_athletes_events %>% 
  filter(Year == 1976 & Season == "Summer") %>%
  group_by(region) %>%
  summarize(Montreal = length(unique(ID)))

data3 <- world %>% left_join(
          tibble(region=unique(world$region))) %>% 
          left_join(montreal, by="region") %>%
          mutate(Montreal = ifelse(is.na(Montreal), 0, Montreal)) 

data3 %>% 
  ggplot(aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Montreal)) +
  labs(title = "The Number of Athletes globally Participated in Montreal 1976",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "lightsteelblue4"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="orchid3") + 
  theme(plot.title = element_text(size = 10,face="bold.italic", color = "red3"),
        legend.title = element_text(size = 8,face="bold.italic", color = "black"),
        legend.text  = element_text(size = 7,face="italic", color = "black")) 

# Moscow 1980 Summer Olympic
moscow <- olympic_athletes_events %>% 
  filter(Year == 1980 & Season == "Summer") %>%
  group_by(region) %>%
  summarize(Moscow = length(unique(ID)))

data4 <- world %>% left_join(
          tibble(region=unique(world$region))) %>% 
          left_join(moscow, by="region") %>%
          mutate(Moscow = ifelse(is.na(Moscow), 0, Moscow)) 

data4 %>% 
  ggplot(aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Moscow)) +
  labs(title = "The Number of Athletes globally Participated in Moscow 1980",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "lightsteelblue4"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="orchid3") + 
  theme(plot.title = element_text(size = 10,face="bold.italic", color = "red3"),
        legend.title = element_text(size = 8,face="bold.italic", color = "black"),
        legend.text  = element_text(size = 7,face="italic", color = "black")) 
```

# Q2:  Since the 2022 Winter Olympics was held this year, what about the development of Alpine Skiing in the Winter Olympics?

## Pic 3
```{r}
p1.1 <- olympic_athletes_events %>% 
      filter(Sport == "Alpine Skiing") %>%
      group_by(Year) %>%
      summarize(Athletes = length(unique(Name)),
                Nations = length(unique(NOC)),
                Events = length(unique(Event))
      ) %>% ggplot(aes(x = Year, y = Nations)) +
      geom_point(size = 2) +
      geom_line() + xlab("")

p2.1 <- olympic_athletes_events %>% 
      filter(Sport == "Alpine Skiing") %>%
      group_by(Year) %>%
      summarize(Athletes = length(unique(Name)),
                Nations = length(unique(NOC)),
                Events = length(unique(Event))
      ) %>% ggplot(aes(x = Year, y = Athletes)) +
      geom_point(size = 2) +
      geom_line() + xlab("")

p3.1 <- olympic_athletes_events %>% 
      filter(Sport == "Alpine Skiing") %>%
      group_by(Year) %>%
      summarize(Athletes = length(unique(Name)),
                Nations = length(unique(NOC)),
                Events = length(unique(Event))
      ) %>% ggplot(aes(x = Year, y = Events)) +
      geom_point(size = 2) +
      geom_line() + xlab("")

tg <- grid::textGrob('Countries attending Apline Skiing Competitions ', gp = gpar(fontsize = 13, fontface = 'bold'))
sg <- textGrob('Attendence Number vs Year', gp = gpar(fontsize = 10))
laym <- matrix(seq_len(5), ncol = 1)
plot_list <- list(p1.1, p2.1, p3.1)
g <- c(list(tg),list(sg),plot_list)
grid.arrange(grobs=g,layout_matrix=laym,heights=c(1,0.7,3,3,3)) 

```

## Pic 4

```{r}
p3.1 <- alpine_skiing %>% group_by(Season, Event) %>%
  summarise(Nations = length(unique(Nation)), 
            # Codexs = length(unique(Codex)),
            Athletes = length(unique(Athlete))) %>%
  ggplot(aes(x = Season, y = Athletes)) + 
  geom_line(color = "grey") + geom_point(aes(color = Event)) +
  xlab("Year") + 
  facet_wrap(~ Event) +
  scale_color_brewer(direction = -1) + theme_dark() +
  labs(title = "The number of athletes attending Alpine Skiing events over times\n four major Alpine Skiing events") + 
  theme(plot.title = element_text(size = 10,face="bold.italic", color = "grey3"),
        axis.title.x = element_text(size = 9,face="bold.italic"),
        axis.title.y = element_text(size = 9,face="bold.italic"),
      legend.title = element_text(size = 8,face="bold.italic", color = "black"),
      legend.text  = element_text(size = 7,face="italic", color = "black")) 

p3.2 <- alpine_skiing %>% group_by(Season, Event) %>%
  summarise(Nations = length(unique(Nation)), 
            # Codexs = length(unique(Codex)),
            Athletes = length(unique(Athlete))) %>%
  ggplot(aes(x = Season, y = Nations)) + 
  geom_line(color = "grey") + geom_point(aes(color = Event)) +
  facet_wrap(~ Event) + xlab("Year") +
  scale_colour_brewer(palette = "Greens") + theme_grey() +
    labs(title = "The number of Nations attending Alpine Skiing events over times\n four major Alpine Skiing events") + 
  theme(plot.title = element_text(size = 10,face="bold.italic", color = "grey3"),
        axis.title.x = element_text(size = 9,face="bold.italic"),
        axis.title.y = element_text(size = 9,face="bold.italic"),
      legend.title = element_text(size = 8,face="bold.italic", color = "black"),
      legend.text  = element_text(size = 7,face="italic", color = "black")) 


p3.0 <- alpine_skiing %>% group_by(Season) %>%
  summarise(Nations = length(unique(Nation)), 
            # Codexs = length(unique(Codex)),
            Athletes = length(unique(Athlete))) %>%
  ggplot(aes(x = Season, y = Athletes)) + 
  geom_line(color = "skyblue3", size = 1) +  #geom_point(aes(color = Event)) +
  # facet_wrap(~ Event) +
  scale_color_brewer(direction = -1) + theme_grey() + 
  xlab("Year") +  ylab("Athlete Number") + 
  theme(axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5))

p3.1
p3.2



```
# Q3: Which countries are the most dominant over the history of Olympics?
## Pic 5

```{r}
# Medals for Olympics
lev_teams2 <- olympic_athletes_events %>% 
  filter(!is.na(Medal))%>% 
  group_by(Team, Medal) %>%
  summarize(Count = length(Medal)) %>%
  group_by(Team) %>%
  summarize(Total = sum(Count)) %>%
  arrange(desc(Total)) %>% select(Team) 

p5.1 <- olympic_athletes_events %>% 
  filter(!is.na(Medal))%>% 
  filter(Team %in% (lev_teams2$Team[1:25])) %>%
  group_by(Team, Medal) %>%
  summarize(Count = length(Medal)) %>%
  mutate(Team = ifelse(is.na(Team), "United States", Team)) %>%
  mutate(Team = forcats::fct_rev(factor(Team, levels = lev_teams2$Team[1:30]))) %>%
  ggplot(aes(Team, Count, fill = Medal)) +
  geom_col() + coord_flip() +
  scale_fill_manual(values = c("palegoldenrod", "plum3", "rosybrown4")) + 
  ggtitle("Historical medal counts for Olympics from 1896 to 2016") +
  theme(plot.title = element_text(size = 9,face="bold.italic"),
        axis.title.x = element_text(size = 9,face="bold.italic"),
        axis.title.y = element_text(size = 9,face="bold.italic"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 8,face="italic"))

# Medals for Alpine Skiing
lev_teams <- olympic_athletes_events %>% 
  filter(!is.na(Medal) & Sport == "Alpine Skiing")%>% 
  group_by(Team, Medal) %>%
  summarize(Count = length(Medal)) %>%
  group_by(Team) %>%
  summarize(Total = sum(Count)) %>%
  arrange(Total) %>% pull(Team)

p5.2 <- olympic_athletes_events %>% 
  filter(!is.na(Medal) & Sport == "Alpine Skiing")%>% 
  group_by(Team, Medal) %>%
  summarize(Count = length(Medal)) %>%
  mutate(Team = factor(Team, levels = lev_teams)) %>%
  ggplot(aes(Team, Count, fill = Medal)) +
  geom_col() + coord_flip() +
  scale_fill_manual(values = c("honeydew1","yellowgreen","turquoise4")) +
  ggtitle("Historical medal counts from Alpine Skiing Competitions") +
  theme(plot.title = element_text(size = 9,face="bold.italic"),
        axis.title.x = element_text(size = 9,face="bold.italic"),
        axis.title.y = element_text(size = 9,face="bold.italic"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 8,face="italic"))
ggplotly(p5.1)
ggplotly(p5.2)
```

## Pic 6

```{r}
medalcount <- olympic_athletes_events %>%
          filter(!is.na(Medal)) %>% 
          group_by(NOC, Medal, Event, Games) %>% 
          summarize(isMedal = 1) %>%
          group_by(NOC, Medal) %>% 
          summarize(medal_count = sum(isMedal)) %>% 
          left_join(noc_regions) %>%
          rename(Team_nation = region) %>% 
          select(Medal, Team_nation, medal_count) %>%
          arrange(desc(medal_count))

world_label <- world %>% 
  group_by(region) %>% 
  mutate(lat = mean(lat), long = mean(long)) %>% 
  select(region, lat, long) %>% 
  unique() %>% ungroup()

world %>% left_join(
    medalcount %>%
    group_by(Team_nation) %>% # Team's total medal number over the years
    summarize(Total = sum(medal_count)) %>% arrange(desc(Total)),
    by = c('region' = 'Team_nation')) %>%
    mutate(label = ifelse(Total < 800, "", region)) %>%
    group_by(region) %>%
    mutate(mean_long = mean(long), mean_lat = mean(lat)) %>%
  ggplot(aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Total)) + 
  labs(x = "", y = "") + 
  scale_fill_gradient(low = "white", high = "darkseagreen4") + 
  ggtitle("Total Number of the Medals that Countries Win Over the Year") + 
  stat_midpoint(aes(label = label, x = mean_long, y = mean_lat), geom = "text",size=2, color = "brown3") +
  theme(plot.title = element_text(size = 9,face="bold.italic", color = "red3"),
        axis.text = element_text(size = 7),
        legend.title = element_text(size = 8,face="bold.italic"),
        legend.text = element_text(size = 8,face="italic"))
  
```
# Q4: What is the Participation Ratio of Men to Women changes over time? Is this ratio increased or decreased?
## Pic 7

```{r}
yeartomod <- olympic_athletes_events %>% 
              select(Year) %>% 
              unique() %>%
              filter((Year %% 4 > 0) & Year != 1906) %>% pull(Year)

olympic_athletes_events %>% 
  mutate(Year = ifelse(Year %in% yeartomod, Year + 2, Year)) %>%
  group_by(Year, Sex) %>%
  summarize(Athlete_number = length(unique(ID))) %>% arrange(Year) %>% 
  ggplot(aes(x = Year, y = Athlete_number, group = Sex, color = Sex)) + 
  geom_point(size = 2) + 
  geom_line() + 
  geom_smooth(method = "loess", formula = 'y ~ x', linetype = 3) + 
  scale_color_manual(values= c("cornflowerblue", "deeppink2")) + 
  theme_classic() + 
  labs(x = "Year", y = "Athlete Number") +
  ggtitle("Athletes attending Olympics over time \nregarding male and female athletes") + 
  theme(plot.title = element_text(size = 10,face="bold.italic", color = "brown3"),
        axis.title.x = element_text(size = 9,face="bold.italic"),
        axis.title.y = element_text(size = 9,face="bold.italic"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 8,face="italic"))  # +  transition_reveal(Year)
```
# Q5: Are athlete’s Age, Height and Weight related to their race results?
## Pic 8:

```{r}
# Intuitively, use PCA to analyse the problem
scaled_olympics <- olympic_athletes_events %>% na.omit() %>%
  select(Team, Sex, Age, Height, Weight, Medal) %>%
  mutate(across(where(is.numeric), ~round((.x-mean(.x))/sd(.x), 2))) %>%
  mutate(Sex = ifelse(Sex == "M", 1, 0))
pca <- prcomp(scaled_olympics[,3:5],center=T, retx=T)
summary(pca)
# Principal Component Loading
mat_round <- function(matrix, n = 3) apply(matrix, 2, function(x) round(x, n))
mat_round(pca$rotation)
pc1 <- paste("PC1 =", paste(round(pca$rotation[,1], 2), "x", rownames(pca$rotation), collapse = " + "))
pc2 <- paste("PC2 =", paste(round(pca$rotation[,2], 2), "x", rownames(pca$rotation), collapse = " + "))
pc1;pc2
```

```{r}
s <- summary(pca)
df_pca <- data.frame(pca$x) %>%
  mutate(Medal = scaled_olympics$Medal)
xlab <- paste("PC 1 (", round(s$importance[2,1]*100, 1), "%)", sep = "")
ylab <- paste("PC 2 (", round(s$importance[2,2]*100, 1), "%)", sep = "")
# use PCA for clustering
scores <- pca$x[,1:2]
k <- kmeans(scores, centers = 3) 
data_pca <- data.frame(scores) %>%
  mutate(cluster = factor(k$cluster), Medal = scaled_olympics$Medal)

# clusters with first 2 principle components
scores <- data.frame(scores) %>%
  mutate(cluster = factor(k$cluster), 
         Medal = scaled_olympics$Medal,
         Team = scaled_olympics$Team)

# Score plot 
ggplot(scores %>% head(25), aes(PC1, PC2, color = Medal, label = Medal)) +
  geom_point() +
  geom_text(nudge_y = .1, size = 2.5) +
  guides(color="none") + # coord_equal() + 
  coord_fixed() +
  ggtitle("Score plot of first two principal components") +
  labs(x = xlab, y = ylab,
       subtitle = "PC1 = -0.21 x Age + -0.69 x Height + -0.7 x Weight\nPC2 = 0.98 x Age + -0.19 x Height + -0.11 x Weight") +
  stat_ellipse(geom = "polygon", aes(fill = Medal),
               alpha = 0.2, 
               show.legend = TRUE,
               level = 00.95) +
  theme(
  plot.title = element_text(color = "red", size = 11, face = "bold"),
  plot.subtitle = element_text(color = "blue", size = 8),
  plot.caption = element_text(color = "green", face = "italic", size = 8),
  legend.title = element_text(color = "grey3", face = "bold.italic", size = 8),
  legend.text = element_text(color = "grey3", face = "italic", size = 8),
  axis.title = element_text(color = "grey3", face = "bold.italic", size = 9),
  axis.text = element_text(color = "grey3", face = "italic", size = 7)
)
```  

- The first two principal components have been contructed as:

1. PC1 = -0.21 x Age + -0.69 x Height + -0.7 x Weight

2. PC2 = 0.98 x Age + -0.19 x Height + -0.11 x Weight

- Medal Results can not be ideally classifed by principal components composed with Age, Weight and Height, concerning the fact that the first two principals have already been efficient in explaining 93.5% information of Age, Weight and Height, yet Medal results still mixed together in the score plot.

```{r}
scaled_olympics[20:31,] %>%
  ggplot(aes(Age, Height, label = Team)) +
  geom_point() +
  geom_abline(slope = pca$rotation[2,1]/pca$rotation[1,1], intercept = 0, color = "mediumpurple") +
  geom_abline(slope = pca$rotation[2,2]/pca$rotation[1,2], intercept = 0, color = "cornflowerblue") +
  annotate("text", x = .45, y = 1.2, label = "PC1", angle = 75, size = 3,
           color = "mediumpurple")  +
  annotate("text", x = -.4, y = 0, label = "PC2", angle = -10, size = 3,
           color = "cornflowerblue") +
  geom_text_repel(nudge_y = .1, size = 2.5) +
  coord_equal() +
  labs(title = "Scatterplot of scaled Olympics data with Principal Components") + 
  theme(
  plot.title = element_text(color = "brown3", size = 10, face = "bold"),
  plot.subtitle = element_text(color = "blue", size = 8),
  plot.caption = element_text(color = "green", face = "italic", size = 8),
  legend.title = element_text(color = "grey3", face = "bold.italic", size = 8),
  legend.text = element_text(color = "grey3", face = "italic", size = 8),
  axis.title = element_text(color = "grey3", face = "bold.italic", size = 9),
  axis.text = element_text(color = "grey3", face = "italic", size = 7)
)
```


```{r warning=FALSE}
p4.1<- olympic_athletes_events %>% 
        mutate(Medal = ifelse(is.na(Medal), "No Medal", Medal)) %>%
        ggplot(aes(x=Medal, y=Age,color=Medal,fill=Sex)) + 
        geom_boxplot()+
        scale_fill_manual(values = c('#999999', '#E69F00', '#56B4E9')) +
        ggtitle("Boxplot for Age vs Medal", subtitle = " -- Concerning Gender") + 
        theme(
            plot.title = element_text(color = "brown3", size = 10, face = "bold.italic"),
            plot.subtitle = element_text(color = "blue", size = 8),
            plot.caption = element_text(color = "green", face = "italic", size = 8),
            legend.title = element_text(color = "grey3", face = "bold.italic", size = 8),
            legend.text = element_text(color = "grey3", face = "italic", size = 8),
            axis.title = element_text(color = "grey3", face = "bold.italic", size = 9),
            axis.text = element_text(color = "grey3", face = "italic", size = 7)
        )
p4.2<- olympic_athletes_events %>%
        mutate(Medal = ifelse(is.na(Medal), "No Medal", Medal)) %>%
        ggplot(aes(x=Medal, y=Height,color=Medal,fill=Sex)) + 
        geom_boxplot()+
        scale_fill_manual(values = c('#999999', '#E69F00', '#56B4E9')) +
        ggtitle("Boxplot for Height vs Medal", subtitle = " -- Concerning Gender") + 
        theme(
            plot.title = element_text(color = "brown3", size = 10, face = "bold.italic"),
            plot.subtitle = element_text(color = "blue", size = 8),
            plot.caption = element_text(color = "green", face = "italic", size = 8),
            legend.title = element_text(color = "grey3", face = "bold.italic", size = 8),
            legend.text = element_text(color = "grey3", face = "italic", size = 8),
            axis.title = element_text(color = "grey3", face = "bold.italic", size = 9),
            axis.text = element_text(color = "grey3", face = "italic", size = 7)
        )
p4.3<- olympic_athletes_events %>% 
        mutate(Medal = ifelse(is.na(Medal), "No Medal", Medal)) %>%
        ggplot(aes(x=Medal, y=Weight,color=Medal,fill=Sex)) + 
        geom_boxplot()+
        scale_fill_manual(values = c('#999999', '#E69F00', '#56B4E9')) +
        ggtitle("Boxplot for Weight vs Medal", subtitle = " -- Concerning Gender") + 
        theme(
            plot.title = element_text(color = "brown3", size = 10, face = "bold.italic"),
            plot.subtitle = element_text(color = "blue", size = 8),
            plot.caption = element_text(color = "green", face = "italic", size = 8),
            legend.title = element_text(color = "grey3", face = "bold.italic", size = 8),
            legend.text = element_text(color = "grey3", face = "italic", size = 8),
            axis.title = element_text(color = "grey3", face = "bold.italic", size = 9),
            axis.text = element_text(color = "grey3", face = "italic", size = 7)
        )
p4.1
p4.2
p4.3
```



